\documentclass{article}

\usepackage[utf8]{inputenc}         % UTF-8 encoding
\setlength{\parindent}{0pt}         % Remove paragraph indentation
\setlength{\parskip}{1em}           % Add spacing between paragraphs

\usepackage{geometry}
\geometry{left=0.5in, right=0.75in, top=0.5in, bottom=0.5in}

% Define metadata
\usepackage{hyperref}
\hypersetup{
    colorlinks=false,
    pdfpagemode={UseNone},
    pdfnonfullscreenpagemode={UseNone},
    pdftitle={Resume},
    pdfauthor={Arron Paul Jeffery},
    pdfsubject={Arron Paul Jeffery},
    pdfcreator={Arron Paul Jeffery},
    pdftrapped={True},
    pdfproducer={Built with LaTeX using GitHub Actions},
    pdfkeywords={Resume; Curriculum vitae; CV; Job application; Professional experience; Skills; Qualifications; Work history; Education; Career; Employment; Job search},
}

% Suppress non-essential metadata
\pdftrailerid{}
\pdfsuppressptexinfo=-1

% Remove page numbers
\pagestyle{empty} 

% Begin
\begin{document}

\begin{center}
    \textbf{\Large Arron Paul Jeffery} \\
    \href{mailto:hello@arron.io}{hello@arron.io} \\
    \href{https://linkedin.com/in/arron-paul}{linkedin.com/in/arron-paul} \\
    +44(0)7593334000
\end{center}

\section*{Summary}

A dedicated and proficient Full-Stack Developer and Software Engineer with over 11 years of experience in application layers, presentation layers, and databases. Skilled in integrating technical expertise with high-level requirements to create fully realised systems.

Passionate about the nuances of software development and digital content creation, I strive to design and develop software that engages users positively, communicates information effectively, and delivers compelling experiences.

\section*{Skills}

Proficient in a wide range of technologies and frameworks, including:

\begin{itemize}
    \item .NET Framework and the Microsoft Web Stack (C\#, ASP.NET Core, Entity Framework)
    \item Cloud Platforms and Services (Azure, Azure DevOps, and Amazon Web Services)
    \item Desktop development (WPF, WinForms, .NET Core)
    \item Web application development (JavaScript, TypeScript, Angular, React, Electron and Node)
    \item Django, Django Rest Framework, and Python
    \item Relational and NoSQL Databases (MySQL, Postgres, MongoDB)
    \item Continuous Integration and delivery automation (Azure DevOps, GitLab CI)
    \item Developer best practices (Branching strategies, code reviews, refactoring, upkeep of documentation, linting \& static analysis functions, clean code, dependency pinning, unit testing, and integration testing where nessessary.)
\end{itemize}

\section*{Experience}

\textbf{2014–2023 Full Stack Web Developer \& Software Engineer} \\
Hexagon AB (formerly Romax Technology), Nottingham, UK
\begin{itemize}
    \item Collaborated with product owners to define issues and gather product requirements. Defined tasks, stories, and their expected durations.
    \item Worked with design teams to produce wireframes for user interfaces, ensuring consistent and accessible UX/UI standards in line with product and brand guidelines.
    \item Coordinated with front-end and back-end teams, mechanical engineers, and other domain-specific teams to deliver high-quality products.
    \item Scrum master. Assumed ownership of sprints for specific products. Mentored junior developers.
    \item Managed DevOps tasks including provisioning VMs, cloud-based infrastructure, and maintaining self-hosted infrastructure.
    \item Adopted modern methodologies such as CI/CD, containerisation, and cloud-based services to enhance the development process.
\end{itemize}

\textbf{Achievements:}
\begin{itemize}
    \item Developed web applications using Python Django, Node.js, Angular, and React for bearing manufacturers to manage proprietary bearing catalogues and perform static analysis functions.
    \item Developed and managed Hexagon’s centralised authentication system (Django) using OAuth2 and JWT.
    \item Contributed to the rationalisation of a monolithic, legacy Smalltalk-based object model by rewriting it in C\# and exposing CRUD operations over REST, enabling the object model to interoperate with web applications (C\# ASP.NET).
    \item Created a solution to migrate historical Zendesk tickets to Jira Service Desk, utilising Zendesk APIs for data retrieval, transforming objects to fit each vendor’s schema, and using Atlassian APIs to recreate tickets.
    \item Contributed to a base application engine, allowing the integration of analysis capabilities through a downstream SDK provided to internal and external users.
    \item Played a key role in migrating legacy applications to the cloud, leveraging Azure DevOps to automate the build and deployment processes.
\end{itemize}

\textbf{2013–2014 Full Stack Web Developer} \\
Romax Insight, Nottingham, UK
\begin{itemize}
    \item Developed fleet monitoring software for wind turbines using Python Django.
    \item Contributed to legacy fleet monitoring software projects using Smalltalk and .NET Framework (C\#).
\end{itemize}

\textbf{2012–2013 Web Developer} \\
Roadtohealth Ltd, Nottingham, UK (Year In Industry)
\begin{itemize}
    \item Designed and implemented web-based frontends for digital health metrics products using PHP, MySQL, and Adobe.
    \item Liaised with customers to implement solutions for support tickets.
\end{itemize}

\section*{Education}

\textbf{2008–2013 Software Engineering BSc. (Hons)} \\
Nottingham Trent University – First Class Honours
\begin{itemize}
    \item Fundamentals: Computer Science (Algorithms, Data Structures, Complexity), CPU Architecture (68K Assembly), Networking (UDP, TCP, OSI model)
    \item Methods: Systems Analysis and Design, Development Lifecycle, Agile, Waterfall, Scrum, TDD
    \item Software: Java, C++ (Game Development, Win32, MFC), SQL \& Rational Database Design
    \item Web Development: PHP, ASP.NET, accessibility (Screen readers, ARIA, WCAG, WAI-ARIA)
    \item Coding practices
\end{itemize}

\textbf{2006–2008 IT Practitioners BTEC National Diploma (Level 3)} \\
NCN New College Nottingham – Merit, Merit, Distinction
\begin{itemize}
    \item Visual Basic 6, Java, Java Swing, static websites with AJAX \& jQuery
\end{itemize}

\textbf{2001–2006 GCSEs} \\
Top Valley Comprehensive School – Double Maths, IT

\section*{Additional Skills}

\section*{Technical Skills}

\begin{itemize}
    \item \textbf{Cloud Platforms and Services:} 
        \begin{itemize}
            \item Azure DevOps, GitHub, GitLab, Atlassian, Heroku (Twelve-factor methodology)
            \item AWS (S3, EC2, CloudFront, RDS, Route53, IAM principals)
            \item Basic knowledge of GCE and Kubernetes
        \end{itemize}

    \item \textbf{Web Development:}
        \begin{itemize}
            \item Frontend: HTML, CSS, JavaScript, TypeScript, Angular, React, NextJS, Jekyll, Microservice architecture
            \item Backend: Node, PHP, ASP.NET, Django, Flask, REST
        \end{itemize}

    \item \textbf{Desktop Development:} 
        \begin{itemize}
            \item Languages: C\#, Visual C++, Java, Python, gRPC
            \item Frameworks: WinUI 3, WPF, XAML, WinForms, .NET Framework, .NET 8, PyQT, Electron
            \item Environments: Objective-C, Cocoa, MFC, Win32
            \item Patterns: DI, MVVM, MVC, Gang of Four.
        \end{itemize}

    \item \textbf{Database Management:}
        \begin{itemize}
            \item MySQL/Maria, Postgres, Amazon RDS, ORMs, GraphQL
        \end{itemize}

    \item \textbf{Mobile Development:} 
        \begin{itemize}
            \item Android development
            \item iOS development with Objective-C (Some Swift)
        \end{itemize}

    \item \textbf{Concepts and Tools:} 
        \begin{itemize}
            \item CI/CD, Git, SVN, DevOps, Black Duck Compliance Compliance with BlackDuck, Code Analysis with SonarQube.
            \item Unix Shell Scripts, PowerShell, PKI Infrastructure \& Codesigning, LDAP, ActiveDirectory.
            \item Docker, Kubernetes, Terraform,
        \end{itemize}
\end{itemize}

\end{document}
